\documentclass[11pt]{article} \usepackage{geometry} % margins
\usepackage{titlesec} % styling sections
\usepackage[fixed]{fontawesome5} % nice icons
\usepackage[svgnames]{xcolor}
\usepackage{hyperref}  % for hyperlinks

% styling parameters >>> Configure page margins with geometry
\geometry{left=1.4cm, top=1cm, right=1.4cm, bottom=1.2cm, footskip=0.5cm}
\hypersetup{
  colorlinks=true,
  allcolors={NavyBlue}
}

\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.3pt]}]
\titlespacing*{\section}{0pt}{0pt}{10pt}
\pagenumbering{gobble}
% <<<

% some formatting macros
\newcommand{\edu}[3]{
  \textbf{#1}\hfill (#2)\\
  #3\vspace{0.7em}}

\newcommand{\jobl}[5]{%
  \textbf{#1}\hfill (#2)\\
  #3\vspace{0.25em}\\
  \textbf{Role:} #4\\
  \textbf{Focus:} #5}

\newcommand{\job}[5]{%
  \jobl{#1}{#2}{#3}{#4}{#5}\vspace{0.5em}
}

\begin{document}
% info header >>>
  \begin{minipage}[c]{0.74\textwidth}
    \centering
    {\LARGE Alexey \textbf{Bochkarev}}\\
    ---\\ 
    Researcher in Mathematical Optimization / Operations Research\\
    PhD candidate, Clemson University
  \end{minipage}\hfill%
  \begin{minipage}{0.26\textwidth}
    \faEnvelope \href{mailto:abochka@g.clemson.edu}{abochka@g.clemson.edu}\\
    \faGlobe \href{https://www.bochkarev.io}{www.bochkarev.io}\\
    \faGithub \href{https://github.com/alex-bochkarev}{alex-bochkarev}\\
    \faTwitter \href{https://twitter.com/a_bochka}{@a\_bochka}\\
    \faTelegram \href{https://t.me/abochka}{@abochka}
  \end{minipage}

 \section*{Research interests and experience}
 Combinatorial optimization, decision diagrams and graphs, network optimization
 and interdiction. Current project aims to apply game playing and reinforcement
 learning techniques to the Dynamic Shortest-path Interdiction problem. Previous
 one dealt with the Consistent Path Problem, trying to get computational edge in
 combinatorial problems by representing binary constraints (e.g., in a variant
 of the Facility Location problem) as Binary Decision Diagrams.
 \textbf{Research supervisor:}
 \href{https://scholar.google.com/citations?user=87CaUHYAAAAJ&hl=en}{Dr. J. Cole
   Smith.}\vspace{0.5em}\\
 \faFile*[regular] \textbf{A. Bochkarev}, J.C. Smith, On Aligning
 Non-Order-Associated Binary Decision Diagrams, revision submitted to \textit{INFORMS
   Journal on
   Computing}. Results presented at INFORMS Annual conference, 2020.\\

 
 \noindent
 \begin{minipage}[t]{0.49\textwidth}
   \section*{Education} 
   \edu{PhD Industrial Engineering}{2018--2021 exp}{
     Clemson University, US. OR track}

   \edu{MSc/BSc Appl. Math and Physics}{2004--2010}{
   Moscow Institute of Physics and Technology, Russia}

   \edu{M.A. Economics}{2008--2010}{
   New Economic School, Russia}
 \section*{Selected coursework}
 \textbf{University:} Mathematical Programming, Network Flows, Algorithms and Data Structures,
 Stochastic Programming intro, Power Markets and Regulations, Game Theory,
 Probability / Statistics, Foundations of Data Science, Calculus \& Co.\vspace{0.5em}

 \textbf{Online:} Analytics Edge (MITx @ EdX), ML basics (Andrew Ng @ Coursera).\\
   \section*{Programming skills}
   \textbf{Main stack:} Python (gurobipy / gurobi, pulp/cbc, numpy, pandas,
   matplotlib/plotly/seaborn), R (ggplot, dplyr, tidyverse), C++, Julia (JuMP)\\
   \textbf{Basic knowledge:} PyTorch, Java, Matlab/Octave\\
   \section*{Other technical skills}
   PBS (comp cluster), GNU/Linux, bash; make, git, \LaTeX, Emacs, basic GIS
   (QGIS), Inkscape, beamer / PPT / LO Impress / reveal.js, Jupyter Notebook.
   \vspace{0.5em}

   \section*{(Human) Languages}
   English (fluent), Russian (native), German (A1).
 \end{minipage}\hfill%
 \begin{minipage}[t]{0.49\textwidth}
   \section*{Teaching experience}
   Designed and delivered  two 4-days mini-courses for gifted
   high-school students and early undergrads: \textit{``Practical Intro to Probability''}
   and \textit{``A Glimplse into Algorithms''}, 2021 (RUS, ENG).

   TA in ``Intro probability'' course, ENG, CU, 2021\vspace{0.3em}

   Other initiatives: ``OR Tech Seminar'' (research toolbox, 4 workshops, 2021)
   
   \section*{Service \& Community}
   \textit{INFORMS Chapter:} Secretary (2020),
   President (2021); 
   ``Journal club on Network optimization and interdiction'' (2021)

   \textit{SMTB, ZPSH:} summer/winter schools for high-school students, 
   instructor (2020, 2021)\\
   
   \section*{Industry experience}
   \job{The Federal Grid (FGC UES)}{2013--2017}{Electricity transmission,
     Moscow, Russia}{Team head: modeling and analytics}{Performance
     benchmarking (branches), operational efficiency improvement. Internal
     regulations/KPI, strategy, analytics, and presentations.}

   \job{Ministry of Energy of Russia}{2013}{Public service: energy
     (electricity), Moscow, Russia}{Deputy team head}{Transmission \&
     distribution grids, benchmarking, economic efficiency.
     Analytics, presentations.}

   \jobl{Roland Berger Strategy Consultants}{2010--2013}{Strategic consulting,
     Moscow, Russia}{ Intern $\rightarrow$ Junior
     Consultant $\rightarrow$ Consultant}{Infrastructure and construction.
     Strategy and performance: market entry, supply/demand modeling, growth
     strategy, efficiency improvement.}
 \end{minipage}
\end{document}